Modern Graph Generators: A Survey

### 2018-10-06 comparison.tex
Minor corrections of the entries in tables

\TODO{Add info to all three tables.}

@@

In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``An.'' stands for graph analytics, ``St.'' stands for graph streaming.} In particular, we show:

\begin{itemize}
\item Characteristics of the domain -- its \textit{type} (fixed, specified using a schema, or extracted from input data) and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain,
\item Characteristics of \textit{read}/\textit{update} operations (if provided), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
\item Key configuration options:
  \begin{itemize}
    \item whether the generator deals only with structure, or also with \textit{properties} of the graph,
    \item supported types of \textit{distributions} used for generating of the data,
    \item \textit{output format} of the produced graph, and
    \item  whether the generator is \textit{distributed} and thus enables more efficient data generation.
  \end{itemize}
\end{itemize}

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part A)} {
\begin{tabular}{| c | p{2.2cm} | p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline   % ====================== general graphs
\multirow{7}{*}{\rot{\textbf{General}}}
  & \cite{barabasi1999emergence} & fixed & & Y & N & Y &  & edge-list &  N  \\
\cline{2-10}
   & R-MAt & fixed & & Y & N & Y & power-law & edge-list &  N  \\
\cline{2-10}
  & GraphGen & fixed & N & Y & N & Y&  & & N   \\
\cline{2-10}
  & Graph 500  & fixed & Various Domains& Y & N & Y & power-law & &  Y  \\
\cline{2-10}
  & BTER & fixed & N &   N &  & N & user-defined & edge-list & Y  \\
\cline{2-10}
  & Darwini & fixed & N &   N &  & N & user-defined &  edge-list & Y   \\
%  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
%\cline{2-10}
\hline
\hline %  ======================  Semantic web
\multirow{20}{*}{\rot{\textbf{Semantic web}}}
 & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
\cline{2-10}
 & LBBM & extracted & Lehigh University BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
\cline{2-10}
 & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
\cline{2-10}
 & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\
\cline{2-10}
 & BSBM & fixed & e-commerce  & fixed & N & Y & mostly normal &  RDF, relational & N   \\
\cline{2-10}
 & SP$^2$Bench & fixed & DBLP  & fixed & N & Y & based on DBLP  & RDF & N   \\
\cline{2-10}
 & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & Y &N & -- &  RDF & N    \\
\cline{2-10}
 & DBPSB & extracted & DBpedia &  templates & N & Y & random &  RDF & N   \\
\cline{2-10}
 & LODIB & fixed & e-commerce &  N & N & Y & 44 types &  RDF & N   \\
\cline{2-10}
 & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\
\cline{2-10}
 & Geographica & fixed & OpenStreetMap  & fixed + templates  & N & Y & -- &  RDF & N   \\
\cline{2-10}
 & WatDiv & schema-driven & user-defined  & templates & N & Y & uniform, normal, Zipfian &  RDF & N   \\
\cline{2-10}
 & RBench & extracted & DBLP, Yago  & templates & N & Y & from real-world data &  RDF & N  \\
\cline{2-10}
 & LDBC SPB & fixed & media  & mixes & N & Y & power law, skewed values, value correlation &  RDF & N  \\
\cline{2-10}
 & LinkGen & schema-driven & user-defined & templates & Y  & N & Gaussian, Zipfian& RDF & N\\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsA}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part B)} {
\begin{tabular}{| c | p{2.2cm}| p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline  % ======================  graph databases
\multirow{7}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
\cline{2-10}
  & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
\cline{2-10}
  & graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
\hline
\hline %  ======================   social networks
\multirow{8}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & impl. not available &  -- \\
\cline{2-10}
 & \cite{Yao2011} & fixed & social network & N & N & N & power-law & impl. not available & --  \\
\cline{2-10}
 & LinkBench & fixed & social network & Y & Y & Y & Facebook & impl. not available & -- \\
\cline{2-10}
 & S3G2 & fixed & social network  & N & N  & Y & Facebook  & CSV, RDF & Y   \\
\cline{2-10}
 & \cite{Sukthankar-SocialInfo2014} & schema-driven & social-network & N & N & Y & power-law & CSV & N   \\
\cline{2-10}
 & LDBC SNB  & fixed & social network &  generated & Y  & Y & Facebook &  CSV, RDF & Y     \\
\cline{2-10}
  & \cite{Nettleton2016} & schema-driven & social network & N & N & Y & power-law & impl. not available & --  \\
%\cline{2-10}
% & SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
%\cline{2-10}
% & Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
\hline
\hline   % ======================   graph analytics
\multirow{3}{*}{\rot{\textbf{Ana.}}}
  & HPC Scalable Graph Analysis & fixed & & Y & N& N& uniform & & N   \\
\cline{2-10}
  & Graphalytics & extracted & social network & Y& N& power law & & & N   \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & schema-driven & Social Network & Y & N & N & user-defined & RDF & N     \\
\cline{2-10}
  & RSPLab & schema-driven & Agnostic & Y & Y & N & user-defined & RDF & N     \\
%\cline{2-10}
%  & & & & & & & &  &   \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsB}
\end{sidewaystable}

@@

\begin{table}[h]
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & \cite{barabasi1999emergence} & {\bf x} & & & & x & \\
\cline{2-8}
   & R-MAt    & {\bf x} & & & & x & \\
\cline{2-8}
  & GraphGen  & {\bf x} & & x & & & \\
\cline{2-8}
  & Graph 500 & {\bf x} & & & & x & \\
\cline{2-8}
  & BTER      & {\bf x} & & & & & \\
\cline{2-8}
  & Darwini   & {\bf x} & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & \\
\cline{2-8}
 & LBBM  & & {\bf x} & & & & \\
\cline{2-8}
 & UOBM  & & {\bf x} & & & & \\
\cline{2-8}
 & IIMB & & {\bf x} & & & & \\
\cline{2-8}
 & BSBM & & {\bf x} & & & & \\
\cline{2-8}
 & SP$^2$Bench & & {\bf x} & & & & \\
\cline{2-8}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & \\
\cline{2-8}
 & DBPSB & & {\bf x} & & & & \\
\cline{2-8}
 & LODIB & & {\bf x} & & & & \\
\cline{2-8}
 & SIB & & {\bf x} & & & & \\
\cline{2-8}
 & Geographica & & {\bf x} & & & & \\
\cline{2-8}
 & WatDiv & & {\bf x} & & & & \\
\cline{2-8}
 & RBench & & {\bf x} & & & & \\
\cline{2-8}
 & LDBC SPB & & {\bf x} & & & & \\
\cline{2-8}
 & LinkGen & & {\bf x} & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & \\
\cline{2-8}
  & gMark & & x & {\bf x} & x & & \\
\cline{2-8}
  & graphGen & & & {\bf x} & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & x & & \\
\cline{2-8}
 & \cite{Yao2011}  & & & & {\bf x} & & \\
\cline{2-8}
 & LinkBench  & & & x & {\bf x} & & \\
\cline{2-8}
 & S3G2  & & x & x & {\bf x} & & \\
\cline{2-8}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & \\
\cline{2-8}
 & LDBC SNB   & & x & x & {\bf x} & & \\
\cline{2-8}
  & \cite{Nettleton2016}  & & & & {\bf x} & & \\
\hline
\hline   % ======================   graph analytics
\multirow{2}{*}{\rot{\textbf{An.}}}
  & HPC Scalable Graph Analysis  & & & & & {\bf x} & \\
\cline{2-8}
  & Graphalytics & & & & & {\bf x} & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & & & & & & {\bf x}\\
\cline{2-8}
  & RSPLab & & & & & & {\bf x} \\
%\cline{2-8}
%  & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

@@

For example, many general or domain-agnostic graph generators such as the
preferential attachment, RMAT or Graph500, are typically used to test graph
analytics framweworks when large real graphs are not available. Actually,
Graphalytics uses RMAT as one as its graph generators for benchmarking graph
analytics.

Similarly, some social network graph generators such as the LDBC-SNB, S3G2 or
LinkBench, can be used to test graph databases. In the case of the first two,
even though they are designed not to be specific to any type of technology,
they graph databases are their main target.  Additionally, they also provide serializers for
RDF, thus they can also be used to test RDF systems.

In the case of LinkBench, nothing prevents the user to load the generated graph
in a graph database (Facebook uses a MySQL in that paper) to
test a workload similar to Facebook and extend and complement it with more
graphy queries like those in LDBC-SNB.

>>>>

@@

In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``An.'' stands for graph analytics, ``St.'' stands for graph streaming. Value $-$ means that the information is not available or relevant.} In particular, we show:

\begin{itemize}
\item Characteristics of the domain -- its \textit{type} (fixed, specified using a schema, or extracted from input data) and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain,
\item Characteristics of \textit{read}/\textit{update} operations (if provided), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
\item Key configuration options:
  \begin{itemize}
    \item whether the generator deals only with structure, or also with \textit{properties} of the graph (Y/N feature),
    \item supported types of \textit{distributions} used for generating of the data,
    \item \textit{output format} of the produced graph, and
    \item  whether the generator is \textit{distributed} and thus enables more efficient data generation (Y/N feature).
  \end{itemize}
\end{itemize}

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part A)} {
\begin{tabular}{| c | p{2.2cm} | p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline   % ====================== general graphs
\multirow{8}{*}{\rot{\textbf{General}}}
  & \cite{barabasi1999emergence} & fixed & & Y & N & Y &  & edge-list &  N  \\
\cline{2-10}
   & R-MAt & fixed & & Y & N & Y & power-law & edge-list &  N  \\
\cline{2-10}
  & GraphGen & fixed & N & Y & N & Y&  & & N   \\
\cline{2-10}
  & Graph 500  & fixed & various domains & Y & N & Y & power-law & &  Y  \\
\cline{2-10}
  & BTER & fixed & N &   N &  & N & user-defined & edge-list & Y  \\
\cline{2-10}
  & Darwini & fixed & N &   N &  & N & user-defined &  edge-list & Y   \\
%  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
%\cline{2-10}
\hline
\hline %  ======================  Semantic web
\multirow{20}{*}{\rot{\textbf{Semantic web}}}
 & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
\cline{2-10}
 & LBBM & extracted & Lehigh university BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
\cline{2-10}
 & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
\cline{2-10}
 & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\
\cline{2-10}
 & BSBM & fixed & e-commerce  & fixed & N & Y & mostly normal &  RDF, relational & N   \\
\cline{2-10}
 & SP$^2$Bench & fixed & DBLP  & fixed & N & Y & based on DBLP  & RDF & N   \\
\cline{2-10}
 & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & Y &N & -- &  RDF & N    \\
\cline{2-10}
 & DBPSB & extracted & DBpedia &  templates & N & Y & random &  RDF & N   \\
\cline{2-10}
 & LODIB & fixed & e-commerce &  N & N & Y & 44 types &  RDF & N   \\
\cline{2-10}
 & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\
\cline{2-10}
 & Geographica & fixed & OpenStreetMap  & fixed + templates  & N & Y & -- &  RDF & N   \\
\cline{2-10}
 & WatDiv & schema-driven & user-defined  & templates & N & Y & uniform, normal, Zipfian &  RDF & N   \\
\cline{2-10}
 & RBench & extracted & DBLP, Yago  & templates & N & Y & from real-world data &  RDF & N  \\
\cline{2-10}
 & LDBC SPB & fixed & media  & mixes & N & Y & power law, skewed values, value correlation &  RDF & N  \\
\cline{2-10}
 & LinkGen & schema-driven & user-defined & templates & Y  & N & Gaussian, Zipfian & RDF & N\\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsA}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part B)} {
\begin{tabular}{| c | p{2.2cm}| p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline  % ======================  graph databases
\multirow{7}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
\cline{2-10}
  & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, Zipfian &  N-triples & N    \\
\cline{2-10}
  & graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
\hline
\hline %  ======================   social networks
\multirow{11}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & impl. not available &  -- \\
\cline{2-10}
 & \cite{Yao2011} & fixed & social network & N & N & N & power-law & impl. not available & --  \\
\cline{2-10}
 & LinkBench & fixed & social network & Y & Y & Y & Facebook & impl. not available & -- \\
\cline{2-10}
 & S3G2 & fixed & social network  & N & N  & Y & Facebook  & CSV, RDF & Y   \\
\cline{2-10}
 & \cite{Sukthankar-SocialInfo2014} & schema-driven & social-network & N & N & Y & power-law & CSV & N   \\
\cline{2-10}
 & LDBC SNB  & fixed & social network &  generated & Y  & Y & Facebook &  CSV, RDF & Y     \\
\cline{2-10}
  & \cite{Nettleton2016} & schema-driven & social network & N & N & Y & power-law & impl. not available & --  \\
%\cline{2-10}
% & SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
%\cline{2-10}
% & Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
\hline
\hline   % ======================   graph analytics
\multirow{3}{*}{\rot{\textbf{Ana.}}}
  & HPC Scalable Graph Analysis & fixed & & Y & N& N& uniform & & N   \\
\cline{2-10}
  & Graphalytics & extracted & social network & Y& N& power law & & & N   \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & schema-driven & social network & Y & N & N & user-defined & RDF & N     \\
\cline{2-10}
  & RSPLab & schema-driven & agnostic & Y & Y & N & user-defined & RDF & N     \\
%\cline{2-10}
%  & & & & & & & &  &   \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsB}
\end{sidewaystable}

@@

\begin{table}[h]
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & \cite{barabasi1999emergence} & {\bf x} & & & & x & \\
\cline{2-8}
   & R-MAt    & {\bf x} & & & & x & \\
\cline{2-8}
  & GraphGen  & {\bf x} & & x & & & \\
\cline{2-8}
  & Graph 500 & {\bf x} & & & & x & \\
\cline{2-8}
  & BTER      & {\bf x} & & & & & \\
\cline{2-8}
  & Darwini   & {\bf x} & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & \\
\cline{2-8}
 & LBBM  & & {\bf x} & & & & \\
\cline{2-8}
 & UOBM  & & {\bf x} & & & & \\
\cline{2-8}
 & IIMB & & {\bf x} & & & & \\
\cline{2-8}
 & BSBM & & {\bf x} & & & & \\
\cline{2-8}
 & SP$^2$Bench & & {\bf x} & & & & \\
\cline{2-8}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & \\
\cline{2-8}
 & DBPSB & & {\bf x} & & & & \\
\cline{2-8}
 & LODIB & & {\bf x} & & & & \\
\cline{2-8}
 & SIB & & {\bf x} & & & & \\
\cline{2-8}
 & Geographica & & {\bf x} & & & & \\
\cline{2-8}
 & WatDiv & & {\bf x} & & & & \\
\cline{2-8}
 & RBench & & {\bf x} & & & & \\
\cline{2-8}
 & LDBC SPB & & {\bf x} & & & & \\
\cline{2-8}
 & LinkGen & & {\bf x} & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & \\
\cline{2-8}
  & gMark & & x & {\bf x} & x & & \\
\cline{2-8}
  & graphGen & & & {\bf x} & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & \\
\cline{2-8}
 & \cite{Yao2011}  & & & & {\bf x} & & \\
\cline{2-8}
 & LinkBench  & & & x & {\bf x} & & \\
\cline{2-8}
 & S3G2  & & x & x & {\bf x} & & \\
\cline{2-8}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & \\
\cline{2-8}
 & LDBC SNB   & & x & x & {\bf x} & & \\
\cline{2-8}
  & \cite{Nettleton2016}  & & & & {\bf x} & & \\
\hline
\hline   % ======================   graph analytics
\multirow{2}{*}{\rot{\textbf{An.}}}
  & HPC Scalable Graph Analysis  & & & & & {\bf x} & \\
\cline{2-8}
  & Graphalytics & & & & & {\bf x} & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & & & & & & {\bf x}\\
\cline{2-8}
  & RSPLab & & & & & & {\bf x} \\
%\cline{2-8}
%  & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

For example, many general or domain-agnostic graph generators such as the
preferential attachment, RMAT or Graph500, are typically used to test graph
analytics frameworks when large real graphs are not available. Actually,
Graphalytics uses RMAT as one as its graph generators for benchmarking graph
analytics.

Similarly, some social network graph generators such as LDBC-SNB, S3G2 or
LinkBench, can be used to test graph databases. In the case of the first two,
even though they are designed not to be specific to any type of technology,
the graph databases are their main target.  Additionally, they also provide serializers for
RDF, thus they can also be used to test RDF systems.

In the case of LinkBench, nothing prevents the user to load the generated graph
in a graph database (Facebook uses MySQL in that paper) to
test a workload similar to Facebook and extend and complement it with more
graph queries like those in LDBC-SNB.

@@
